---
title: "Experiment 1 analysis"
author: "Alan Jern and Stephen Payne"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lme4)
library(afex)
library(here)
```

```{r}
expt_data <- read_csv("../Results/Rater/Tidy/rater-tidy-experiment-12-09-21.csv") %>%
  mutate(Context = as_factor(Context)) %>%
  mutate(Subject = as.character(Subject)) %>%
  mutate(Context = recode(Context,
                          "1" = "relevant",
                          "2" = "non-relevant"))

```


```{r}


m <- lmer(formula = Rating ~ 1 + Context * Level +
            (1|Story) + 
            (1 + Level|Subject), 
          data = expt_data)

summary(m)


```


## Interpreting results

The main things we're interested in here:
* Main effect of level: This shows the effect of level when context is social
* Interaction: We expect a sig. interaction here. Specifically, we expect a negative interaction, which would mean that the slope of the level variable would be adjusted down when context is non-relevant. This makes sense because we assume basically a horizontal line for ratings across levels for non-relevant context, but a roughly increasing line for ratings across levels for relevant context.

```{r}

library(Hmisc)
library(ggsci)

set.seed(123)
ggplot(data = expt_data,
       aes(x = TVal, color = Context, y = Rating)) +
  geom_jitter(aes(y = Rating),
              alpha = 0.4,
              width = 2) +
  stat_summary(fun.data = "mean_cl_boot", size = 1.3) +
  facet_wrap(vars(Story), scales = "free") +
  scale_y_continuous(breaks = c(1:7),
    labels = c("1","2","3","4","5","6","7"),
    minor_breaks = NULL) +
  # TODO: Change x-tick labels to actual t levels (need to look up how to do this)
  scale_x_continuous(minor_breaks = NULL) +
  scale_color_d3() +
  theme(legend.position = "bottom") +
  labs(
    x = "t"
  )


```


```{r}

# Split data into the three separate stories
cake_data <- expt_data %>% filter(Story == "cake")
movie_data <- expt_data %>% filter(Story == "movie")
podcast_data <- expt_data %>% filter(Story == "podcast")

# Fit a linear model for each story to the ratings
lm_cake <- lm(formula = Rating ~ TVal, data = cake_data)
lm_movie <- lm(formula = Rating ~ TVal, data = movie_data)
lm_podcast <- lm(formula = Rating ~ TVal, data = podcast_data)

# Create data frames with inferred (predicted) ratings for all
# t values

# Note, you can change the values for which these data frames
# generate predicted values by changing the range of TVal
# in the call to 'expand_grid'
inferred_cake_ratings <- expand_grid(TVal = 1:120) 
inferred_cake_ratings <- inferred_cake_ratings %>%
  mutate(predicted_rating = predict(lm_cake, inferred_cake_ratings))


inferred_movie_ratings <- expand_grid(TVal = 1:180) 
inferred_movie_ratings <- inferred_movie_ratings %>%
  mutate(predicted_rating = predict(lm_movie, inferred_movie_ratings))

inferred_podcast_ratings <- expand_grid(TVal = 1:250) 
inferred_podcast_ratings <- inferred_podcast_ratings %>%
  mutate(predicted_rating = predict(lm_podcast, inferred_podcast_ratings))

```


Export ratings as CSV files
```{r}
write.csv(inferred_cake_ratings, file="./interpolatedContextRatings/interpolatedCakeRatings.csv", row.names = FALSE)
write.csv(inferred_podcast_ratings, file="./interpolatedContextRatings/interpolatedPodcastRatings.csv", row.names = FALSE)
write.csv(inferred_movie_ratings, file="./interpolatedContextRatings/interpolatedMovieRatings.csv", row.names = FALSE)
```